\documentclass{scrartcl}

\usepackage{tumbase}
\usepackage[@TEXTFONT@, @MATHFONT@]{tumfonts}

\usepackage[math]{blindtext}
\usepackage{csquotes}

% imaginary units i, j, and k
\renewcommand*{\i}{\ensuremath{\mathrm{i}}}
\renewcommand*{\j}{\ensuremath{\mathrm{j}}}
\renewcommand*{\k}{\ensuremath{\mathrm{k}}}


\begin{document}

\section{Manual test}

This is an example text. And here are some equations to test the mathematical
font, for example, the famous Schrödinger equation
\begin{equation}
  \mathrm{i} \hbar \partial_t \Psi = \hat H \Psi.
\end{equation}

Vectors may assume different forms, either with arrow or similar symbol on
top ($\vec E$, $\vec r_0$, ...) or in bold math font ($\mathbf{E}$,
$\mathbf{r}_0$).

In particular, it is important that inline mathematical expression such as
the short equation $a^2 + b^2 = c^2$ and numbers $\approx 1, 2, 3$ blend in
nicely.
This is assumed to be difficult with sans serif fonts such as Helvetica. And
what about greek letters ($\alpha$, $\beta$, $\gamma$, $\Delta$, $\xi$,
$\Xi$, ...) or calligraphic letters ($\mathcal{L}$, $\mathcal{H}$,
$\mathcal{M}$, ...) or fraktur letters ($\mathfrak{su}$) or Hebrew letters
($\aleph$, $\beth$, ...)?

Further examples are Maxwell's equations in 1D
\begin{subequations}
  \begin{align}
    \partial_t E_z & = \epsilon^{-1}
    \left( -\sigma E_z - \partial_t P_z + \partial_x H_y \right), \\
    \partial_t H_y & = \mu^{-1} \partial_x E_z,
  \end{align}
\end{subequations}
or the von Neumann equation for a two-level quantum mechanical system
\begin{subequations}
  \begin{align}
    \partial_t \Delta & = -4\Omega_\mathrm{R} \rho_i - \tau_1^{-1}
    \left( \Delta - \Delta_0 \right),                                      \\
    \partial_t \rho_r & = \omega_{12} \rho_i - \tau_{2}^{-1} \rho_r,       \\
    \partial_t \rho_i & = -\omega_{12} \rho_r + \Omega_\mathrm{R} \Delta -
    \tau_{2}^{-1} \rho_i,
  \end{align}
\end{subequations}
here written as set of elementwise differential equations.

Of course, also monospace text is quite interesting, in particular in
programming. Here, one usually writes command in the command line in this
font,
for example, \texttt{ls -al gunter}, where \texttt{gunter} may be a file or a
directory.

\section{Helvetica test}

Certain parts (e.g., TUM threeliner in header) require Helvetica in both
cases.

\begingroup
\fontfamily{phv}\selectfont
This paragraph must be in Helvetica. This paragraph must be in Helvetica.
This paragraph must be in Helvetica.
\endgroup

\section{Blind math paper}

\blindmathpaper

\subsection{Blindtext}
Dies ist ein Typoblindtext. An ihm kann man sehen, ob alle Buchstaben da sind
und wie sie aussehen. Manchmal benutzt man Worte wie Hamburgefonts,
Rafgenduks oder Handgloves, um Schriften zu testen. Manchmal Sätze, die alle
Buchstaben des Alphabets enthalten - man nennt diese Sätze
\enquote{Pangrams}. Sehr bekannt ist dieser: The quick brown fox jumps over
the lazy old dog. Oft werden in Typoblindtexte auch fremdsprachige Satzteile
eingebaut (AVAIL\textregistered\ and Wefox\texttrademark\ are testing aussi
la Kerning), um die Wirkung in anderen Sprachen zu testen. In Lateinisch
sieht zum Beispiel fast jede Schrift gut aus. Quod erat demonstrandum. Seit
1975 fehlen in den meisten Testtexten die Zahlen, weswegen nach TypoGb. 204 §
ab dem Jahr 2034 Zahlen in 86 der Texte zur Pflicht werden. Nichteinhaltung
wird mit bis zu 245 \texteuro\ oder 368 \textdollar\ oder 173 \textsterling\
bestraft. Genauso wichtig in sind mittlerweile auch Â\c{c}cè\~{n}t\"{e}, die
in neueren Schriften aber fast immer enthalten sind. Ein wichtiges aber
schwierig zu integrierendes Feld sind OpenType-Funktionalitäten. Je nach
Software und Voreinstellungen können eingebaute Kapitälchen, Kerning oder
Ligaturen (sehr pfiffig) nicht richtig dargestellt werden.
\textcopyright~Blindtext Generator

\section{Font size comparison}

\subsection{Text font families and shapes}

Comparison of serif and sans serif text fonts. They should match in size and
appearance\\
A\textsf{A}B\textsf{B}C\textsf{C}D\textsf{D}E\textsf{E}F\textsf{F}G\textsf{G}
H\textsf{H}I\textsf{I}J\textsf{J}K\textsf{K}L\textsf{L}M\textsf{M}N\textsf{N}
O\textsf{O}P\textsf{P}Q\textsf{Q}R\textsf{R}S\textsf{S}T\textsf{T}U\textsf{U}
V\textsf{V}W\textsf{W}X\textsf{X}Y\textsf{Y}Z\textsf{Z}\\
a\textsf{a}b\textsf{b}c\textsf{c}d\textsf{d}e\textsf{e}f\textsf{f}g\textsf{g}
h\textsf{h}i\textsf{i}j\textsf{j}k\textsf{k}l\textsf{l}m\textsf{m}n\textsf{n}
o\textsf{o}p\textsf{p}q\textsf{q}r\textsf{r}s\textsf{s}t\textsf{t}u\textsf{u}
v\textsf{v}w\textsf{w}x\textsf{x}y\textsf{y}z\textsf{z}\\\\
Comparison of serif and typewriter text fonts\\
A\texttt{A}B\texttt{B}C\texttt{C}D\texttt{D}E\texttt{E}F\texttt{F}G\texttt{G}
H\texttt{H}I\texttt{I}J\texttt{J}K\texttt{K}L\texttt{L}M\texttt{M}N\texttt{N}
O\texttt{O}P\texttt{P}Q\texttt{Q}R\texttt{R}S\texttt{S}T\texttt{T}U\texttt{U}
V\texttt{V}W\texttt{W}X\texttt{X}Y\texttt{Y}Z\texttt{Z}\\
a\texttt{a}b\texttt{b}c\texttt{c}d\texttt{d}e\texttt{e}f\texttt{f}g\texttt{g}
h\texttt{h}i\texttt{i}j\texttt{j}k\texttt{k}l\texttt{l}m\texttt{m}n\texttt{n}
o\texttt{o}p\texttt{p}q\texttt{q}r\texttt{r}s\texttt{s}t\texttt{t}u\texttt{u}
v\texttt{v}w\texttt{w}x\texttt{x}y\texttt{y}z\texttt{z}\\\\
All sans serif and all typewriter alphabet\\
{\sffamily ABCDEFGHIJKLMNOPQRSTUVWXYZ\\ abcdefghijklmnopqrstuvwxyz
0123456789}\\
{\ttfamily ABCDEFGHIJKLMNOPQRSTUVWXYZ\\ abcdefghijklmnopqrstuvwxyz
0123456789}

\subsection{Math alphabet and main text font}

Main text font and math font should have equal height and depth. Also the
stroke width and overall appearance should match to ensure a harmonic look\\
A$A$B$B$C$C$D$D$E$E$ F$F$G$G$H$H$I$I$J$J$ K$K$L$L$M$M$N$N$O$O$
P$P$Q$Q$R$R$S$S$T$T$ U$U$V$V$W$W$X$X$Y$Y$Z$Z$\\
a$a$b$b$c$c$d$d$e$e$ f$f$g$g$h$h$i$i$j$j$ k$k$l$l$m$m$n$n$o$o$
p$p$q$q$r$r$s$s$t$t$ u$u$v$v$w$w$x$x$y$y$z$z$\\
0$0$1$1$2$2$3$3$4$4$5$5$6$6$7$7$8$8$9$9$

\subsection{Greek alphabet}

Greek upper case letters\\
$\mathrm{AB}\Gamma\Delta \mathrm{EZH}\Theta \mathrm{IK}\Lambda\mathrm{MN}$
$\Xi\mathrm{O}\Pi\mathrm{P} \Sigma\mathrm{T}\Upsilon\Phi$
$\mathrm{X}\Psi\Omega$
\\
\\Greek lower case letters\\
$\alpha\beta\gamma\delta \epsilon\varepsilon\zeta\eta$
$\theta\vartheta\iota\kappa \lambda\mu\nu\xi o\pi\varpi\rho$
$\varrho\sigma\varsigma\tau \upsilon\phi\varphi\chi \psi\omega$ \\
\\Proper math fonts also provide italic upper case greek letters\\
$AB\varGamma\varDelta EZH\varTheta IK\varLambda MN\varXi O\varPi P\varSigma$
$T\varUpsilon\varPhi X\varPsi\varOmega$ \\
\\Very good math fonts might also provide upright lowercase Greek letters\\
$\upalpha\upbeta\upgamma\updelta\upepsilon\upvarepsilon\upzeta\upeta\uptheta$
$\upvartheta\upiota\upkappa\uplambda\upmu\upnu\upxi$
$o\uppi\upvarpi\uprho\upvarrho\upsigma\upvarsigma\uptau\upupsilon\upphi$
$\upvarphi\upchi\uppsi\upomega$\\
\\Greek letters should match the Latin letters in height and depth\\
$a\alpha b\beta c\gamma d\delta e\epsilon\varepsilon f\zeta g\eta$
$h\theta\vartheta i\iota jk\kappa\varkappa l\lambda m\mu n\nu\xi\pi\varpi$
$op\rho\varrho qrs\sigma\varsigma t\tau uv\upsilon owx\chi y\psi z\omega$

\subsection{Check important math symbols}

A collection of important math symbols that should be provided by any font\\
$\forall \exists \nexists \in \ni \notin \infty \propto \partial \nabla$
$\dagger\ddagger \emptyset\varnothing \aleph$ $\hbar h \imath i\i \jmath$
$j\j$\\
$+-\pm\mp \cdot\times\ast\circ\div / =\neq\equiv\approx\sim$
$<>\ll\gg\leq\geq\leqq\geqq$
$\subset\supset\nsupseteq\subseteq\supseteq\subsetneq\supsetneq$
$\cup\cap \vee\wedge\neg \perp\parallel$ \\
$\oplus\ominus\otimes\oslash\odot\circledcirc\circledast$
$\leftarrow\rightarrow\leftrightarrow\uparrow\downarrow\updownarrow$
$\Leftarrow\Rightarrow\Leftrightarrow\Uparrow\Downarrow\Updownarrow$
$\rightleftarrows\rightleftharpoons\dots\vdots\cdots\ddots$

\subsection{Check additional math alphabets}
$\mathbb{C}\mathbb{R}\mathbb{Q}\mathbb{Z}\mathbb{N}\mathbb{1}$\\
$\mathcal{ABCDEFGHIJKLMNOPQRSTUVWXYZ}$\\
$\mathfrak{ABCDEFGHIJKLMNOPQRSTUVWXYZ}$\\
$\mathfrak{abcdefghijklmnopqrstuvwxyz}$

\end{document}
